Reanalysis Step 4: Propensity Score Analysis with Twang

### 2025-09-12 reanalysis-4-propensity_scores.qmd
balance stat

# Display average
cat("\n**Average of largest absolute SMDs across imputations:**", round(avg_largest_smd, 4), "\n")
cat("**Number of valid SMD values:**", n_valid_smds, "out of", n_imputations, "\n")

if (avg_largest_smd < 0.1) {
  cat("**Interpretation:** Excellent balance (avg largest |SMD| < 0.1)\n")
} else if (avg_largest_smd < 0.25) {
  cat("**Interpretation:** Good balance (avg largest |SMD| < 0.25)\n") 
} else {
  cat("**Interpretation:** Poor balance (avg largest |SMD| ≥ 0.25) - consider alternative methods\n")
}
```

>>>>

# Display average
if (!is.na(avg_largest_smd)) {
  cat("\n**Average of largest absolute SMDs across imputations:**", round(avg_largest_smd, 4), "\n")
} else {
  cat("\n**Average of largest absolute SMDs across imputations:** NA (unable to extract SMDs)\n")
}
cat("**Number of valid SMD values:**", n_valid_smds, "out of", n_imputations, "\n")

if (!is.na(avg_largest_smd)) {
  if (avg_largest_smd < 0.1) {
    cat("**Interpretation:** Excellent balance (avg largest |SMD| < 0.1)\n")
  } else if (avg_largest_smd < 0.25) {
    cat("**Interpretation:** Good balance (avg largest |SMD| < 0.25)\n") 
  } else {
    cat("**Interpretation:** Poor balance (avg largest |SMD| ≥ 0.25) - consider alternative methods\n")
  }
} else {
  cat("**Interpretation:** Unable to assess balance - SMD extraction failed\n")
}
```
